---
title: "Lab 00 - Hello IDS!"
author: "Carissa"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Miranda", "Freddie", "Connor", 
           "Jenny", "Maya"),
  github_username = c("mirandamonascal", "facott", "Coshea46", 
                      "yoaging-w", "MayaSmaoui"), 
  colour = c("maroon", "green", "green", 
             "purple", "yellow"),
  hobby = c("drums", "hockey", "judo", 
            "walking", "piano"),
  favourite_number = c(2, 1, 8, 4, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The bar chart shows each person's favourite colour plotted against their favourite number.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "username", 
          y = "favourite_number",
          title = "colour_by_number")
```

I think that the command labs() creates a bar chart or a diagrammatic representation of the data and labels the axes and gives it a title.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

The data can be displayed using a table or pie chart.
